---
title: "Dev-Coop-Test"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dev-Coop-Test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.width=6, fig.height=6
)
```

```{r setup}
#install.packages("finnsurveytext")
#library(finnsurveytext)
devtools::load_all() # TO-DO: remove this load_all() line and uncomment the library() line. 
```


## Description
We're looking at FSD2821 Young People's Views on Development Cooperation 2012

FSD2821 Nuorten ajatuksia kehitysyhteistyöstä 2012

[q11_1] Jatka lausetta: Kehitysmaa on maa, jossa... (Avokysymys)
[q11_2] Jatka lausetta: Kehitysyhteistyö on toimintaa, jossa... (Avokysymys)
[q11_3] Jatka lausetta: Maailman kolme suurinta ongelmaa ovat... (Avokysymys)

(Translations)
[q11_1] Continue the sentence: A developing country is a country where... (Open question)
[q11_2] Continue the sentence: Development cooperation is an activity in which... (Open question)
[q11_3] Continue the sentence: The world's three biggest problems are... (Open question)

## Read in 

```{r}
# devdata <- read.csv('//ad.helsinki.fi/home/a/adeclark/Documents/data/FSD2821/Study/Data/daF2821.csv', sep = ';')

devdata <- dev_data

q11_1 <- fst_prepare_conllu(data = devdata, field = "q11_1", stopword_list = "nltk")
q11_2 <- fst_prepare_conllu(data = devdata, field = "q11_2", stopword_list = "nltk")
q11_3 <- fst_prepare_conllu(data = devdata, field = "q11_3", stopword_list = "nltk")
```

## EDA

### Summarise
```{r}
fst_summarise(q11_1)
fst_summarise(q11_2)
fst_summarise(q11_1)
```

### POS Summary
```{r}
fst_pos(q11_1)
fst_pos(q11_2)
fst_pos(q11_3)
```

### Top Words
```{r}
fst_freq(q11_1, 10, c("NOUN", "VERB", "ADJ", "ADV"))
fst_freq(q11_2, 10, c("NOUN", "VERB", "ADJ", "ADV"))
fst_freq(q11_3, 10, c("NOUN", "VERB", "ADJ", "ADV"))
```

### Bi-grams and Trigrams 

```{r}
fst_ngrams(q11_1, number = 10, ngrams=2)
fst_ngrams(q11_1, number = 10, ngrams=3)

fst_ngrams(q11_2, number = 10, ngrams=2)
fst_ngrams(q11_2, number = 10, ngrams=3)

fst_ngrams(q11_3, number = 10, ngrams=2)
fst_ngrams(q11_3, number = 10, ngrams=3)
```

### Wordcloud
```{r}
fst_wordcloud(q11_1, pos_filter = c("NOUN", "VERB", "ADJ", "ADV"))
fst_wordcloud(q11_2, pos_filter = c("NOUN", "VERB", "ADJ", "ADV"))
fst_wordcloud(q11_3, pos_filter = c("NOUN", "VERB", "ADJ", "ADV"))

```

### Exploring some concept networks based on thematic frequently occuring words
Mostly not setting threshold because there are only ~950 responses
#### Q11_1
[q11_1] Jatka lausetta: Kehitysmaa on maa, jossa... (Avokysymys)
[q11_1] Continue the sentence: A developing country is a country where... (Open question)

* standard of living, poor, man
```{r}
fst_concept_network(q11_1, concepts = "elintaso, köyhä")
fst_concept_network(q11_1, concepts = "elintaso, köyhä", threshold = 3)
fst_concept_network(q11_1, concepts = "elintaso, köyhä, ihminen")
fst_concept_network(q11_1, concepts = "elintaso, köyhä, ihminen", threshold = 3)
```

#### Q11_2
[q11_2] Jatka lausetta: Kehitysyhteistyö on toimintaa, jossa... (Avokysymys)
[q11_2] Continue the sentence: Development cooperation is an activity in which... (Open question)

* development, help, strive, country, man
```{r}
fst_concept_network(q11_2, concepts = "kehitysmaa, auttaa, pyrkiä, maa, ihminen")
fst_concept_network(q11_2, concepts = "kehitysmaa, auttaa, pyrkiä, maa, ihminen", threshold = 10)
fst_concept_network(q11_2, concepts = "kehitysmaa, auttaa, pyrkiä, maa, ihminen", threshold = 5)

fst_concept_network(q11_2, concepts = "kehitysmaa, auttaa, pyrkiä")
fst_concept_network(q11_2, concepts = "kehitysmaa, auttaa, pyrkiä", threshold = 5)

```

#### Q11_3
[q11_3] Continue the sentence: The world's three biggest problems are... (Open question)
[q11_3] Continue the sentence: The world's three biggest problems are... (Open question)

* poverty, famine, war, climate change, lack of
```{r}
fst_concept_network(q11_3, concepts = "köyhyys")
fst_concept_network(q11_3, concepts = "köyhyys, puute")
fst_concept_network(q11_3, concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute") 
fst_concept_network(q11_3, concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute", threshold = 3)
fst_concept_network(q11_3, concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute", threshold = 2)
```

