---
title: "Tutorial2-Data_exploration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial2-Data_exploration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.width=6, fig.height=6
)
```

## Introduction

Exploratory Data Analysis (EDA) is a common activity once data has been cleaned and prepared. EDA involves running functions which allow you to better understand the responses and begin to formulate initial hypotheses based on the data. 

This tutorial follows on from Tutorial 1 and guides you through an EDA of data which has been prepared into CoNLL-U format. These EDA functions are contained in `r/02_data_exploration.R`.

The included functions are: 

1. `fst_summarise_short`
2. `fst_summarise`
3. `fst_pos`
4. `fst_length_summary`
5. `fst_get_top_words`
6. `fst_get_top_ngrams`
7. `fst_get_top_ngrams2`
8. `fst_freq_plot`
9. `fst_ngrams_plot`
10. `fst_wordcloud`
12. `fst_freq`
13. `fst_ngrams`

First, install and load the `finnsurveytext` package as below:
(Other required packages such as `dplyr` and `stringr` will also be installed if they are not currently installed in your environment.)

```{r setup}
library(finnsurveytext)
```

There are two sets of data files available within the package which could be used in this tutorial. These files have been created following the process demonstrated in Tutorial 1. The suffixes 'iso', 'nltk' and 'snow' refer to the stopword list used within the preparation activities. 

### 1. Child Barometer Data
* data/conllu_cb_bullying.rda
* data/conllu_cb_bullying_iso.rda

### 2. Development Cooperation Data
* data/conllu_dev_q11_1.rda
* data/conllu_dev_q11_1_nltk.rda
* data/conllu_dev_q11_1_snow.rda
* data/conllu_dev_q11_2.rda
* data/conllu_dev_q11_2_nltk.rda
* data/conllu_dev_q11_3.rda
* data/conllu_dev_q11_3_nltk.rda

You can read these in as follows: 

```{r}
bullying <- conllu_cb_bullying_iso
knitr::kable(head(bullying))
q11_1 <- conllu_dev_q11_1_nltk
```

### Get Summary Table
`fst_summarise_short` and `fst_summarise`

This first function creates a simple summary table for the data that shows the total number of word, number of unique words, and number of unique lemmas in the data. You can either view the table in the console, or define a variable which will contain this table. 

The second function adds information about the number and proportion of survey respondents which answered this question

```{r}
fst_summarise_short(bullying)

q11_1_summary_table <- fst_summarise(q11_1, 'All')
knitr::kable(q11_1_summary_table)
```

`fst_summarise_short` and `fst_summarise` take 1 argument:

1. `data` is output from data preparation, prepared data in CoNLL-U format, such as the output of `fst_prepare_connlu`.

`fst_summarise` takes an optional second argument:

2. `desc` is an optional string describing respondents. If not defined, it will default to 'All respondents'.  

### Get Part-Of-Speech Summary Table
`fst_pos`

This function creates a table which counts the number of words of each part-of-speech (POS) tag within the data. Again, you can either view the table in the console, or define a variable which will contain this table.

```{r}
fst_pos(bullying)

q11_1_pos_table <- fst_pos(q11_1)
knitr::kable(q11_1_pos_table)
```

`fst_pos` takes 1 argument:

1. `data` is output from data preparation, prepared data in CoNLL-U format, such as the output of `fst_prepare_connlu`.


### Get Length Summary Table
`fst_length_summary`

This function creates a table which summarises the distribution of lengths in the responses. Again, you can either view the table in the console, or define a variable which will contain this table.

```{r}
fst_length_summary(bullying, desc = 'All Bullying Respondents')

q11_1_length_table <- fst_length_summary(q11_1, incl_sentences = FALSE)
knitr::kable(q11_1_length_table)
```

`fst_length_summary` takes 3 argument:

1. `data` is output from data preparation, prepared data in CoNLL-U format, such as the output of `fst_prepare_connlu`.
2. `desc` is an optional string describing respondents. If not defined, it will remain blank in the table.  
3. `incl_sentences` is a boolean of whether to include sentence data in table, default is `TRUE`

## Top Words and N-grams Tables

Next we will demonstrate some functions which are used to create plots of most frequent words and n-grams occurring in the data. An n-gram is a set of n successive words in the data. 

### Make Top Words/N-grams Tables
`fst_get_top_words` and `fst_get_top_ngrams`

These functions creates a table of the most frequently occurring words/n-grams in the data (noting that "stopwords" may have been removed in previous data preparation steps.) 

The top words/n-grams tables are able have the word/n-grams normalised if you choose. The variable `norm` is the method for normalising the data. Valid settings are `'number_words'` (the number of words in the responses, default), `'number_resp'` (the number of responses), or `NULL` (raw count returned).

Optionally, you can indicate which POS tags to include. (`fst_get_top_words` and `fst_get_top_ngrams` print a message. There is a third function `fst_get_top_ngrams2` which doesn't print a message. This function is used within the comparison functions in `04_comparison_functions.R`)

We run the functions as follows:

```{r}
fst_get_top_words(bullying)

fst_get_top_words(data = bullying,
         number = 15,
         norm = NULL,
         pos_filter = c("NOUN", "VERB", "ADJ", "ADV"),
         strict = FALSE)

table1 <- fst_get_top_words(q11_1, 5)
knitr::kable(table1)

table2 <- fst_get_top_words(q11_1, 5, 'number_resp', c("NOUN", "VERB"), strict = FALSE)
knitr::kable(table2)

fst_get_top_ngrams(bullying, ngrams = 2)

fst_get_top_ngrams(bullying, ngrams = 2, norm = 'number_words', strict = FALSE)

table3 <- fst_get_top_ngrams(q11_1, 15, ngrams = 3)
knitr::kable(table3)

table4 <- fst_get_top_ngrams(q11_1, 15, ngrams = 2, pos_filter = c("NOUN", "VERB"), strict = FALSE)
knitr::kable(table4)

```

`fst_get_top_words` takes 4 arguments:

1. `data` is output from data preparation, prepared data in CoNLL-U format, such as the output of `fst_prepare_connlu`.
2. `number` is the number of top words/n+grams to return, default is `10`.
3. `norm` is the method for normalising the data. Valid settings are `'number_words'` (the number of words in the responses, default), `'number_resp'` (the number of responses), or `NULL` (raw count returned).
4. `pos_filter` is an optional list of which POS tags to include such as `'c("NOUN", "VERB", "ADJ", "ADV")'`. The default is `NULL`, in which case all words in the data are considered.
5. `strict` is a boolean that determines how the function will deal with 'ties'. If `strict = TRUE`, the table will cut-off at the exact `number`(words are presented in alphabetical order so later-alphabetically, equally occurring words to the word at `number` will not be shown.) If `strict = FALSE`, the table will show any words that occur equally frequently as the number cutoff word. 

`fst_get_top_ngrams` has an additional argument: 

5. `ngrams` is the type of n-grams. The default is "1" (so top words). Set `ngrams = 2` to get bigrams and `n = 3` to get trigrams etc. 

### Make Top Words/N-grams Tables
`fst_freq_plot` and `fst_ngrams_plot`

These functions plot the results of `fst_get_top_words` and `fst_get_top_ngrams`.

```{r}
fst_freq_plot(table1, number = 5, name = 'Table 1')
fst_ngrams_plot(table1, number = 5, ngrams = 1, 'Table 1 with N-grams Plot Function')

fst_ngrams_plot(table3, number = 15, ngrams = 3, 'Trigrams')
fst_ngrams_plot(table4, number = 15, ngrams = 2, 'Bigrams')
```

The arguments are: 

1. `table` is the output of `fst_get_top_words` or `fst_get_top_ngrams`
2. `number` The number of words/n-grams, default is `10`.
3. `name` is an optional "name" for the plot, default is `NULL`

Again, `fst_get_top_ngrams` has an additional argument: 

5. `ngrams` is the type of n-grams. As you can see above, you can plot top words using `ngrams = 1`.

### Find and Plot Top Words/N-grams
`fst_freq` and `fst_ngrams`

These functions run `fst_get_top_words`/`fst_get_top_ngrams` and `fst_freq_plot`/`fst_ngrams_plot` within one function:

```{r}
fst_freq(q11_1, number = 12, strict = FALSE, name = "Q11_1")
fst_ngrams(bullying, number = 12, ngrams = 2)
```

The arguments are as defined in the above functions: 

1. `data`
2. `number`
3. (`ngrams`)
4. `norm`
5. `pos_filter`
6. `strict`
7. `name`


### Make Wordcloud
`fst_wordcloud`

This function will create a wordcloud plot for the data. There is an option to select only specific word types (POS tag).

```{r}
fst_wordcloud(bullying)
fst_wordcloud(q11_1,
              pos_filter = c("NOUN", "VERB", "ADJ", "ADV"), 
              max = 150)
```

`fst_wordclouds` takes 3 arguments:

1. `data` is output from data preparation, prepared data in CoNLL-U format, such as the output of `fst_prepare_connlu`.
2. `pos_filter` is an optional list of POS tags for inclusion in the wordcloud. The defaul is `NULL`.
3. `max` is the maximum number of words to display, the default is `100`. 

## Conclusion
EDA of open-ended survey questions can be conducted using functions in `r/02_data_exploration.R` such as finding most frequent words and n-grams, summarising the length of responses and words used, and visualising responses in word clouds. The results of this EDA can help researchers better understand their data, create hypotheses based on this initial insights, and inform future analysis of the surveys. 

## Citation

The Office of Ombudsman for Children: Child Barometer 2016 [dataset]. Version 1.0 (2016-12-09). Finnish Social Science Data Archive [distributor]. http://urn.fi/urn:nbn:fi:fsd:T-FSD3134

Finnish Children and Youth Foundation: Young People's Views on Development Cooperation 2012 [dataset]. Version 2.0 (2019-01-22). Finnish Social Science Data Archive [distributor]. http://urn.fi/urn:nbn:fi:fsd:T-FSD2821
