---
title: "Tutorial6-Example of analysis of an open-ended survey question"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Q11_3-Story}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.width=6, fig.height=6
)
```

```{r setup}
library(finnsurveytext)
```

## Introduction

This tutorial demonstrates the use of the package to analyse a survey question. It is intended to demonstrate the use of the package from start to finish in detail. In this example, we look at responces split by gender but it is expected that you might look at a variety of different splits of your data in analysis. 

### The question

We will look at our Q11_3 data from the Development Cooperation 2012 survey data which is included as sample data with our package. The specific question we're looking at is as follows:

* [q11_3] Jatka lausetta: Maailman kolme suurinta ongelmaa ovat... (Avokysymys)
  + [q11_3] Continue the sentence: The world's three biggest problems are... (Open question)

Below, we prepare the data. (For further explanation of these functions, see Tutorial1-Prepare CoNLL-U.)
```{r}
all <- fst_prepare_conllu(data = dev_data, field = "q11_3", stopword_list = "none")
all_nltk <- fst_prepare_conllu(data = dev_data, field = "q11_3", stopword_list = "nltk")
female <- fst_prepare_conllu(data = dev_data_f, field = "q11_3", stopword_list = "none")
female_nltk <- fst_prepare_conllu(data = dev_data_f, field = "q11_3", stopword_list = "nltk")
male <- fst_prepare_conllu(data = dev_data_m, field = "q11_3", stopword_list = "none")
male_nltk <- fst_prepare_conllu(data = dev_data_m, field = "q11_3", stopword_list = "nltk")
na <- fst_prepare_conllu(data = dev_data_na, field = "q11_3", stopword_list = "none")
na_nltk <- fst_prepare_conllu(data = dev_data_na, field = "q11_3", stopword_list = "nltk")
```

The following is an excerpt from one of our prepared datasets:
```{r}
knitr::kable(head(all_nltk, 10))
```

First, let's consider all the data to get some initial information about the responses to this question:

```{r}
knitr::kable(
  fst_summarise(all_nltk)
)

knitr::kable(
  fst_pos(all_nltk)
)

knitr::kable(
  fst_length_summary(all_nltk)
)
```

#### Remarks:

* We have an overall response rate of 97%. We might wonder, is this response rate consist across different types of survey participants?
* Responses consist mostly of adjectives (10% of words in stopwords-removed responses), nouns (80%) and verbs (7%)
* Responses to this question are between 1 and 32 words, and between 1 and 3 sentences. Mos responses seem to be 1 sentence with an average of 4-5 words


```{r}
fst_wordcloud(all_nltk)
```

#### Remarks:

* Top words seem to be 'nälänhätä', 'köyhyys', 'sota'
* Next tier of common words might be: 'vesi' 'puute', 'ihminen', 'ilmastonmuutos', 'ahneus', 'nälka', 'epätasa-arvo'

##### Translations

* 'köyhyys' poverty
* 'nälänhätä' famine
* 'sota' war
* 'vesi' water
* 'puute' lack of 
* 'ihminen' human
* 'ilmastonmuutos' climate change
* 'ahneus' greed
* 'nälka' hunger
* 'epätasa-arvo' inequality

```{r}
fst_freq(all_nltk, 10, strict = FALSE)
fst_ngrams(all_nltk, 10, ngrams = 2, strict = FALSE)
fst_ngrams(all_nltk, 10, ngrams = 3, strict = FALSE)
```

#### Remarks: 

* We see the top words we identified previously
* We get more context on 'vesi' here. This makes sense since 'water' alone doesn't describe a common international 'problem'.  
  + 'puhdas vesi' clean water
  + 'vesi puute' lack of water
* We can assume that answers like 'nälänhätä sota' are probably from listing different terms in responses. So, some bigrams are more meaningful than others. 

### A Concept Network

Next, let's look at some concept networks before we look into gender.
Our concept network function can be used to visualise the words that occur around our words of interest

```{r}
fst_concept_network(all_nltk, 
                    concepts = "köyhyys, nälänhätä, sota", 
                    title = "Q11_3 - No threshold") 
fst_concept_network(all_nltk, concepts = "köyhyys, nälänhätä, sota", 
                    threshold = 5, 
                    title = "Q11_3 - Threshold = 5") 
fst_concept_network(all_nltk, 
                    concepts = "köyhyys, nälänhätä, sota", 
                    threshold = 3, 
                    title = "Q11_3 - Threshold = 3") 
```

#### Remarks: 
* The 'no threshold' graph seems the most meaningful here. 
* We can see that our top three words, in red, are highly related to each other in use. 
* We can see the relationship between 'vesi' with 'puute' and 'puhdas' in this plot. 

Now, let's add more words in:

```{r}
fst_concept_network(all_nltk, 
                    concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute, ihminen, vesi, epätasa-arvo", 
                    title = "Q11_3 - Lots of words") 
fst_concept_network(all_nltk, 
                    concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos, puute, ihminen, vesi, epätasa-arvo", 
                    title = "Q11_3 - Lots of words, threshold = 3", threshold = 5) 
```

#### Remarks:
* The 'no-threshold' plot here is very busy. When we introduce a threshold, the plot splits in two which indicates that the two groups of words are only "connected" in a few responses. 

Now, let's see what do people who talk about water tend to also say in their responses: 
```{r}
fst_concept_network(all_nltk, concepts = "vesi", title = "Q11_3 - Vesi") 
fst_concept_network(all_nltk, concepts = "puute, puhdas, vesi", title = "Q11_3 - ") 
```

#### Remarks: 
* Again, we see the strong relationship with 'puute' and 'puhdas' with some other, less-frequent words too. 

# Split by gender

Now we've looked at responses as a whole, we consider whether gender impacts word choice. 

```{r}
knitr::kable(
  fst_summarise_compare(female_nltk, male_nltk, na_nltk, all_nltk, name1 = 'F', name2 = 'M', name3= 'NA', name4 = 'All')
)

knitr::kable(
  fst_pos_compare(female_nltk, male_nltk, na_nltk, all_nltk, name1 = 'F', name2 = 'M', name3= 'NA', name4 = 'All')
)

knitr::kable(
  fst_length_compare(female_nltk, male_nltk, na_nltk, all_nltk, name1 = 'F', name2 = 'M', name3= 'NA', name4 = 'All')
)
```

#### Remarks: 
* Relatively consistent response rate, slightly higher (98%) response rate for females
* Very consistent distribution across word type! - slightly less nouns (75%) in NA but this is a much smaller sample
* Lengths of responses are similar across cohorts

Let's do comparison cloud and individual word clouds (second comp cloud in case NA data is too small)

```{r}
fst_comparison_cloud(data1 = female_nltk, name1 = 'Female', 
                    data2 = male_nltk, name2 = 'Male', 
                    data3 = na_nltk, name3 = 'NA', 
                    max = 50)

fst_comparison_cloud(data1 = female_nltk, name1 = 'Female', 
                    data2 = male_nltk, name2 = 'Male', 
                    max = 50)

fst_wordcloud(female_nltk)
fst_wordcloud(male_nltk)
fst_wordcloud(na_nltk)
```

Based on comparison cloud, it looks like: 

* top words ("köyhyys, nälänhätä, sota") common in all 3. 
* 'epätasa-arvo' associated with female, 'ilmastonmuutos' associated with males 

When we look at individuals, we see: 

* 'ilmastonmuutos' in top 3 for males - possibly # 2, nälnhätä less common for males 
* evident less data for NA

#### N-grams and top words

Here, we will exclude the responses with 'NA' for gender as we go on, as there are very few of these. 
```{r}
fst_freq_compare(data1 = female_nltk, name1 = 'Female',
                 data2 = male_nltk, name2 = 'Male', 
                 data3 = na_nltk, name3 = 'NA',
                 number = 5, 
                 pos_filter = NULL,
                 unique_colour = 'indianred', 
                 strict = TRUE)

fst_freq_compare(data1 = female_nltk, name1 = 'Female',
                 data2 = male_nltk, name2 = 'Male', 
                 number = 10, 
                 pos_filter = NULL,
                 unique_colour = 'indianred', 
                 strict = TRUE)


fst_ngrams_compare(data1 = female_nltk, name1 = 'Female',
                 data2 = male_nltk, name2 = 'Male',
                 number = 10,
                 ngrams = 2,
                 pos_filter = NULL,
                 unique_colour = 'indianred', 
                 strict = TRUE)

```

Here we see that male and female respondents have the same top 4 words, but that 'nälänhätä' is more frequent for females than males, and 'ilmastonmuutos' conversely. This may prompt further research into whether male survey participants show more concern about climate change than females in the remainder of the survey,

For the bigrams, we can identify that
* both genders frequently list lack of water but it is mostly females who mention *clean* water.
* males respondents rate climate change higher 

#### Concept network of top 4 words

Now, we'll look at the concept network for the 4 top words in female and male responses. 
These words are 'sota', 'köyhyys', nälänhätä', and 'ilmastonmuutos'.

```{r}
fst_concept_network_compare(data1 = female_nltk, name1 = 'Female',
                            data2 = male_nltk, name2 = 'Male', 
                            concepts = "köyhyys, nälänhätä, sota, ilmastonmuutos", threshold = 1)

```

Interestingly, our concept network plots of these top 4 words show that there is a much larger variety of terms used by female respondents who mention these 4 common responses.

Only part of this is explained by the fact that we have nearly 4 times as many responses from female participants since each of these plots have their vertex weights determined from only their cohort’s responses. Therefore, there may be other subgroups within the male respondents who discuss independent themes to these.

## Conclusion 

This tutorial demonstrates the use of `finnsurveytext` to look at a single question and then consider whether gender impacts response. Gender is just one of many ways you could split the data and is used as an example in this context. It is likely an analyst would want to split the data in other ways also such as age, education level, etc. 

Following the use of `finnsurveytext`, we have a number of hypotheses, such as "Male survey respondents are more concerned about climate change than females", which could inform further analysis of the survey as a whole. 

## Citation

Finnish Children and Youth Foundation: Young People's Views on Development Cooperation 2012 [dataset]. Version 2.0 (2019-01-22). Finnish Social Science Data Archive [distributor]. http://urn.fi/urn:nbn:fi:fsd:T-FSD2821

