---
title: "Tutorial5-Demonstration_of_comparison_functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial5-Demonstration_of_comparison_functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8, fig.height = 6
)
```

## Introduction
When analysing responses to open-ended questions, you may want to look into whether different groups of survey participants have, in general, responded differently to the prompt. `finnsurveytext` contains a number of comparison functions which are intended to be used to compare responses between groups. These comparison functions covered are defined in `r/04_comparison_functions.R` and `r/05_comparison_concept_network.R`.

One way to split the data is using a different question within the survey such as a categorical question (eg. gender or level of education) or an ordinal variable (such as aged or income). In this tutorial, we will look at comparing responses to a question based on gender. Before using the comparison functions, we run the preparation functions which are in `r/01_prepare_conll-u.R` (and which are covered in detail in 'Tutorial1-Prepare CoNLL-U') for each group separately.  

The comparison functions are: 

1. `fst_get_unique_ngrams`
2. `fst_join_unique`
3. `fst_ngrams_compare_plot`
4. `fst_ngrams_compare_plot2`
5. `fst_plot_multiple`
6. `fst_freq_compare`
7. `fst_ngrams_compare`
8. `fst_pos_compare`
9. `fst_summarise`
10. `fst_summarise_compare`
11. `fst_length_compare`
12. `fst_comparisoncloud`
13. `fst_cn_get_unique`
14. `fst_cn_compare_plot`
15. `fst_concept_network_compare`

We will look at the following question: 

* [q11_2] Jatka lausetta: Kehitysyhteistyö on toimintaa, jossa... (Avokysymys)
  + (In English) [q11_2] Continue the sentence: Development cooperation is an activity in which... (Open question)

First, install and load the `finnsurveytext` package as below:
(Other required packages such as `dplyr` and `stringr` will also be installed if they are not currently installed in your environment.)

```{r setup}
library(finnsurveytext)
```

There are four sets of data files available within the package which are used in this tutorial

### Development Cooperation Data Split by Gender
* data/dev_data.rda - All responses to the survey
* data/dev_data_m.rda - Responses to the survey by participants who have listed their gender as male 
* data/dev_data_f.rda - Responses to the survey by participants who have listed their gender as female 
* data/dev_data_na.rda - Responses to the survey by participants who have not responded to the gender question 

We can prepare the data into CoNLL-U format using functions from `01_prepare_conllu-u.R` as follows:
(We are preparing versions with and without stopwords removed because we have some functions which are better with/without the stopwords included.)

```{r}
all <- fst_prepare_conllu(data = dev_data, field = "q11_2", stopword_list = "none")
all_nltk <- fst_prepare_conllu(data = dev_data, field = "q11_2", stopword_list = "nltk")
female <- fst_prepare_conllu(data = dev_data_f, field = "q11_2", stopword_list = "none")
female_nltk <- fst_prepare_conllu(data = dev_data_f, field = "q11_2", stopword_list = "nltk")
male <- fst_prepare_conllu(data = dev_data_m, field = "q11_2", stopword_list = "none")
male_nltk <- fst_prepare_conllu(data = dev_data_m, field = "q11_2", stopword_list = "nltk")
na <- fst_prepare_conllu(data = dev_data_na, field = "q11_2", stopword_list = "none")
na_nltk <- fst_prepare_conllu(data = dev_data_na, field = "q11_2", stopword_list = "nltk")

knitr::kable(head(male_nltk))
```

Now that our data is ready, we can look at our data and compare the results. 

First, we will look at some summary functions to compare the responses overall. (We are using the versions which **include** the stopwords here.) 

#### Make Comparison Summary
Consider the definition of `fst_summarise_compare`:
```{r eval=FALSE}
# fst_summarise_compare <- function(data1,
#                                   data2,
#                                   data3 = NULL,
#                                   data4 = NULL,
#                                   desc1 = "Group 1",
#                                   desc2 = "Group 2",
#                                   desc3 = "Group 3",
#                                   desc4 = "Group 4")
```

We can run this function for our data: 
(we use `knitr::kable` function below to display results in a "prettier" table)
```{r}
knitr::kable(
  fst_summarise_compare(
    data1 = all, name1 = "All",
    data2 = female, name2 = "Female",
    data3 = male, name3 = "Male",
    data4 = na, name4 = "Unspecified"
  )
)
```

We can already see that our data is quite unbalanced. There are a lot more female respondents than male or unspecified. The response (to this question) rate is high (97%) but slightly lower for the unspecified respondents. Unsurprisingly, since there are more female responses, the female responses to this question contain a larger variety of words. 

Next, we will look at part-of-speech tags and lengths of responses. 

Consider the definition of `fst_pos_compare` and `fst_length_compare`:
```{r eval=FALSE}
# fst_pos_compare <- function(data1,
#                             data2,
#                             data3 = NULL,
#                             data4 = NULL,
#                             name1 = "Group 1",
#                             name2 = "Group 2",
#                             name3 = "Group 3",
#                             name4 = "Group 4")
#
# fst_length_compare <- function(data1,
#                                data2,
#                                data3 = NULL,
#                                data4 = NULL,
#                                name1 = "Group 1",
#                                name2 = "Group 2",
#                                name3 = "Group 3",
#                                name4 = "Group 4",
#                                incl_sentences = TRUE)
```

We run the functions to look further into the differences between the respondent types. 
```{r}
knitr::kable(
  fst_pos_compare(
    data1 = all, name1 = "All",
    data2 = female, name2 = "Female",
    data3 = male, name3 = "Male",
    data4 = na, name4 = "Unspecified"
  )
)

knitr::kable(
  fst_length_compare(
    data1 = all, name1 = "All",
    data2 = female, name2 = "Female",
    data3 = male, name3 = "Male",
    data4 = na, name4 = "Unspecified"
  )
)
```

In terms of POS tags, the scale differences are likely mostly due to the differences in the number of respondents between genders. We can also see that female responses are generally slightly longer (average of 6 words to 5 words) but that most respondents (across the genders) wrote only a single sentence.

### Comparison Cloud

Now that we've looked at the overview comparisons, we will create a comparison cloud between the responses, using the versions with stopwords removed so that only more meaningful words remain.

Consider the definition of `fst_comparisoncloud`:
```{r eval=FALSE}
# fst_comparisoncloud(data1,
#                     data2,
#                     data3 = NULL,
#                     data4 = NULL,
#                     name1 = "Group 1",
#                     name2 = "Group 2",
#                     name3 = "Group 3",
#                     name4 = "Group 4",
#                     pos_filter = NULL,
#                     max = 100)
```

We create our comparison cloud as follows: 
```{r}
fst_comparison_cloud(
  data1 = female, name1 = "Female",
  data2 = male, name2 = "Male",
  data3 = na, name3 = "Unspecified",
  max = 50
)
```

A comparison cloud compares the relative frequency with which a term is used in two or more documents. This cloud shows words that occur more regularly in responses from a specific type of respondent. For more information about comparison clouds, you can read [this documentation](https://cran.r-project.org/web/packages/wordcloud/wordcloud.pdf). 

Our data is quite unbalanced (there are a lot more female respondents and fewer 'NA' so this may skew responses) but it seems that a higher proportion of these 'NA' respondents use 'ihminen' and 'auttaa' in their responses. Similarly, 'raha' and 'yrittää' are associated with males and females respectively.  

### Common Words and N-grams
Now, we will look at common words occurring in the responses. 

Consider first the definition of `fst_get_top_words` and `fst_get_top_ngrams`:

```{r eval=FALSE}
# fst_get_top_words <- function(data,
#                               number = 10,
#                               norm = 'number_words',
#                               pos_filter = NULL,
#                               strict = TRUE)
#
# fst_get_top_ngrams <- function(data,
#                                number = 10,
#                                ngrams = 1,
#                                norm = 'number_words',
#                                pos_filter = NULL, strict = TRUE)
```


First, we will consider all the responses for this question. We are not filtering the data based on POS tag, and will leave the default of `strict = TRUE` which will cut-off the list at 10 words (see the warning note about this). We also use the default for the norm which means we are standardising between groups by dividing count of a word by the total number of words in the responses. 

```{r}
all_top10 <- fst_get_top_words(all_nltk,
  number = 10,
  norm = "number_words",
  pos_filter = NULL,
  strict = FALSE
)
all_top10bigrams <- fst_get_top_ngrams(all_nltk,
  number = 10,
  ngrams = 2,
  norm = "number_words",
  pos_filter = NULL,
  strict = TRUE
)

knitr::kable(all_top10)
knitr::kable(all_top10bigrams)
```

Now we will look at top words by gender: 
```{r}
female_top10 <- fst_get_top_words(female_nltk,
  number = 10,
  norm = "number_words",
  pos_filter = NULL,
  strict = TRUE
)
knitr::kable(female_top10)

male_top10 <- fst_get_top_words(male_nltk,
  number = 10,
  norm = "number_words",
  pos_filter = NULL,
  strict = TRUE
)
knitr::kable(male_top10)

na_top10 <- fst_get_top_words(na_nltk,
  number = 10,
  norm = "number_words",
  pos_filter = NULL,
  strict = TRUE
)
knitr::kable(na_top10)
```

As you can see, the top words are very similar across all respondent types. 

This is further shown in the plots. (Note that words that are unique to a gender are highlighted in red. This is only comparing the top 10 words, so be aware this word likely still appears in the other genders, just less frequently!)
```{r}
fst_freq_compare(
  data1 = female_nltk, name1 = "Female",
  data2 = male_nltk, name2 = "Male",
  data3 = na_nltk, name3 = "Unspecified",
  number = 10,
  norm = "number_words",
  pos_filter = NULL,
  unique_colour = "indianred",
  strict = TRUE
)

fst_ngrams_compare(
  data1 = female_nltk, name1 = "Female",
  data2 = male_nltk, name2 = "Male",
  data3 = na_nltk, name3 = "Unspecified",
  number = 10,
  ngrams = 2,
  norm = "number_words",
  pos_filter = NULL,
  unique_colour = "indianred",
  strict = TRUE
)
```

Now, we might want to compare this to the overall results. Since, `fst_freq_compare` looks for unique words among all the sets provided, and we only want to look for unique words within the gender-specific sets, we need to run this activity through the component functions. (Just for fun, let's also changed the colour of the unique words.)

```{r}
unique <- fst_get_unique_ngrams(female_top10, male_top10, na_top10)

female_top10u <- fst_join_unique(female_top10, unique)
male_top10u <- fst_join_unique(male_top10, unique)
na_top10u <- fst_join_unique(na_top10, unique)

plot_all <- fst_freq_plot(all_top10, number = 10, name = "All")
plot_f <- fst_ngrams_compare_plot(female_top10u,
  ngrams = 1,
  number = 10,
  override_title = "Female",
  unique_colour = "purple"
)
plot_m <- fst_ngrams_compare_plot(male_top10u,
  ngrams = 1,
  number = 10,
  override_title = "Male",
  unique_colour = "magenta"
)
plot_na <- fst_ngrams_compare_plot(na_top10u,
  ngrams = 1,
  number = 10,
  override_title = "Unspecified",
  unique_colour = "aquamarine"
)

fst_plot_multiple(plot_all,
  plot_f,
  plot_m,
  plot_na,
  main_title = "Top Words By Gender"
)
```


Since the top 3 words are 'kehitysmaa', 'auttaa', and 'pyrkiä', we will create concept networks based on these terms.

The comparison concept network function is defined as follows: 

```{r eval=FALSE}
# fst_concept_network_compare <- function(data1,
#                                         data2,
#                                         data3 = NULL,
#                                         data4 = NULL,
#                                         pos_filter = NULL,
#                                         name1 = "Group 1",
#                                         name2 = "Group 2",
#                                         name3 = "Group 3",
#                                         name4 = "Group 4",
#                                         concepts,
#                                         norm = 'number_words',
#                                         threshold = NULL)
```

We run it as below. Again, we're keeping the default norm. 
```{r}
fst_concept_network_compare(
  data1 = female_nltk, name1 = "Female",
  data2 = male_nltk, name2 = "Male",
  data3 = na_nltk, name3 = "Unspecified",
  concepts = "kehitysmaa, auttaa, pyrkiä"
)
```

As you can see, this can result in a plot that is too busy (especially in the markdown format where we've limited the size of the plots). 

Let's try again with just male and female data. 

```{r}
fst_concept_network_compare(
  data1 = female_nltk, name1 = "Female",
  data2 = male_nltk, name2 = "Male",
  concepts = "kehitysmaa, auttaa, pyrkiä"
)
```

Each of these Concept Networks are created separately, which means that the weights of words are based only on the responses within that gender. Despite this, we have many more words in the female plot (possibly due to there being more responses in this data leading to increased variation). Below, we will run the female with stricter thresholds. (Note, the threshold works on the RAW count of co-occurences between words, not on the normalised co-occurrence value). 

```{r}
fst_concept_network(female_nltk,
  concepts = "kehitysmaa, auttaa, pyrkiä",
  threshold = NULL,
  title = "No Threshold"
)

fst_concept_network(female_nltk,
  concepts = "kehitysmaa, auttaa, pyrkiä",
  threshold = 5,
  title = "Threshold = 5"
)
```


Now let's manually create the concept networks so that there is a requirement of at least 4 occurrences for words in the female network (there are ~3.7x as many females as males so I have chosen 4). These networks look more comparable now and we can see that the concept networks show different words used around our "concept" words of "kehitysmaa", "auttaa" and  "pyrkiä" by female respondents than male. 

```{r}
concepts <- "kehitysmaa, auttaa, pyrkiä"
female_edges <- fst_cn_edges(female_nltk, concepts, threshold = 4)
male_edges <- fst_cn_edges(male_nltk, concepts)

female_nodes <- fst_cn_nodes(female_nltk, female_edges)
male_nodes <- fst_cn_nodes(male_nltk, male_edges)

unique2 <- fst_cn_get_unique(female_nodes, male_nodes)

female_cn <- fst_cn_compare_plot(female_edges, female_nodes, concepts,
  unique_lemmas = unique2,
  name = "Female",
  concept_colour = "red", unique_colour = "purple"
)

male_cn <- fst_cn_compare_plot(male_edges, male_nodes, concepts,
  unique_lemmas = unique2,
  name = "Male",
  concept_colour = "red", unique_colour = "blue"
)

fst_plot_multiple(plot1 = female_cn, plot2 = male_cn, main_title = "Comparison Plot of Female and Male Respondences Q11_2")
```

## Conclusion
As demonstrated in this tutorial, `finnsurveytext` contains a number of functions which can be used to compare responses between groups. This analysis could form the start of further work into the responses to question 11_2 by respondents based on their gender, or as just one of many different splits used to investigate the responses. 

## Citation

Finnish Children and Youth Foundation: Young People's Views on Development Cooperation 2012 [dataset]. Version 2.0 (2019-01-22). Finnish Social Science Data Archive [distributor]. http://urn.fi/urn:nbn:fi:fsd:T-FSD2821
